\cvsection{Work Experience}
\begin{cventries}
  \cventry
    {Computer Science Departament}
    {Part-Time Professor}
    {Valparaíso, Chile}
    {Jul. 2016 - Present}
    {
      \begin{cvitems}
        \item {Propose and teach a new course called Software Deployment on Linux. Some tools that we used were: Docker, Kubernetes, AWS, Django, PHP,  and Nginx. As a result, the students acquired practical and useful skills to deploy their applications.}
        \item {Teach the course Operating System. In this course, the students practically learned the concepts using a Linux environment and related tools such as strace and perf.}
      \end{cvitems}
    }
    
    
  \cventry
    {Chilean Virtual Observatory (ChiVO)}
    {DevOps}
    {Valparaíso, Chile}
    {Jan. 2018 - May. 2018}
    {
      \begin{cvitems}
        \item {DevOps in the Jovial porject, a Cloud service where astronomers can safely use Jupyter notebooks over a personal space designed for high-performance processing under the high-availability principle.}
      \end{cvitems}
    }
    

  \cventry
    {Linets}
    {Systems Engineer}    
    {Santiago, Chile}
    {Jan. 2014 - Mar. 2016}
    {
      \begin{cvitems}
        \item {System Administrator for the internal servers and primary Level 3 support for all the clients}
        \item {Work with OpenStack and all its components to build the first OpenStack deployment in Chile which backs Beebop the first public cloud in Chile.}
        \item {Automatic Deployment of OpenStack using Docker Containers and Ansible playbooks}
        \item {Design and implementation of Ceph Cluster}
      \end{cvitems}
    }
    
  \cventry
    {Computer Science Departament}
    {Systems Administrator}    
    {Valparaíso, Chile}
    {Aug. 2011 - Oct. 2014}
    {
      \begin{cvitems}
		\item{System Administrator for the internal servers}
      \end{cvitems}
    }    
\end{cventries}
